Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-15 paper/introduction.tex
Review changes; minor issues.

Automatic annotation by segmentation and classification of brain tissue is
challenging~\cite{isbi_challenge} and all available methods make errors. This
requires that the results are being \emph{proofread} by humans. This crucial
task serves two purposes: 1) to correct errors in the segmentation, and 2) to
increase the body of labeled data from which to train better automatic
segmentation methods. Recent proofreading tools provide intuitive user
interfaces to browse segmentation data in 2D and 3D and to identify and manually
correct errors~\cite{markus_proofreading,raveler,mojo2,haehn_dojo_2014}. Many
kinds of errors exist, such as inaccurate boundaries, but the most common are
\emph{split errors}, where a single segment is labeled as two, and \emph{merge
errors}, where two segments are labeled as one
(Fig.~\ref{fig:merge_and_slit_errors}). With user interaction, split errors can
be joined, and the missing boundary in a merge error can be defined with
manually-seeded watersheds~\cite{haehn_dojo_2014}. However, the visual
inspection to find errors takes the majority of the time, even with
semi-automatic correction tools~\cite{proofreading_bottleneck}.

@@

Our goal is to automatically detect split and merge errors to reduce visual
inspection time. Further, to reduce correction time we wish to propose
corrections to the user to accept or reject. We call this process \textit{guided
proofreading}.

We learn a classifier for split errors with a convolutional neural network
(CNN). This takes as input patches of membrane segmentation probabilities, cell
segmentation masks, and boundary masks, and outputs a probability score. As we
must process large data, this classifier only operates on cell boundaries, which
reduces computation over methods that analyze every pixel. For merge errors, we
invert and reuse the split classification network, instead asking it to rate a
set of generated candidate boundaries that hypothesize a split. We compute
corrections for both types of errors.

We also propose a greedy algorithm for guided proofreading. Possible erroneous
regions are sorted by their score, and a correction is generated for each
region. Then, a user works through this list of regions and corrections. In a
forced choice setting, the user either selects a correction or skips it to
advance to the next region. In an automatic setting, errors with a high
probability can be automatically corrected first, given an appropriate
probability threshold, after which the user would take over. Finally, to test
the limits of performance, we create an oracle that only accepts corrections
improving the segmentation based on knowledge of the ground truth. This equals
perfect proofreading.

@@

In this paper, we make the following contributions.
%
First, we present a CNN-based boundary classifier for split errors, plus a merge
error classifier that inverts the split error classifier. This is used to
propose merge error corrections, removing the need to manually draw the missing
edge. These classifiers perform well without much training data, which is
expensive to collect for connectomics data.
%
Second, we developed a guided proofreading approach to correcting segmentation
volumes, and an assessment scenario comparing forced-choice interaction with
automatic and oracle proofreading.
%
Furthermore, we present the results of a quantitative user study assessing
guided proofreading, which shows that our method is able to reduce segmentation
error faster than state-of-the-art semi-automatic tools for both novice and
expert users.
%
Our method is applicable to all existing automatic segmentation methods that
produce a label map. As such, we believe that guided proofreading is a promising
direction to proofread segmentations more efficiently to better tackle large
volumes of connectomics imagery.

>>>>

Automatic annotation by segmentation and classification of brain tissue is
challenging~\cite{isbi_challenge} and all available methods make errors, so 
the results must be \emph{proofread} by humans. This crucial
task serves two purposes: 1) to correct errors in the segmentation, and 2) to
increase the body of labeled data from which to train better automatic
segmentation methods. Recent proofreading tools provide intuitive user
interfaces to browse segmentation data in 2D and 3D and to identify and manually
correct errors~\cite{markus_proofreading,raveler,mojo2,haehn_dojo_2014}. Many
kinds of errors exist, such as inaccurate boundaries, but the most common are
\emph{split errors}, where a single segment is labeled as two, and \emph{merge
errors}, where two segments are labeled as one
(Fig.~\ref{fig:merge_and_slit_errors}). With user interaction, split errors can
be joined, and the missing boundary in a merge error can be defined with
manually-seeded watersheds~\cite{haehn_dojo_2014}. However, the visual
inspection to find errors takes the majority of the time, even with
semi-automatic correction tools~\cite{proofreading_bottleneck}.

@@

Our goal is to automatically detect split and merge errors to reduce visual
inspection time. Further, to reduce correction time, we propose
corrections to the user to accept or reject. We call this process \textit{guided
proofreading}.

We learn a classifier for split errors with a convolutional neural network
(CNN). This takes as input patches of membrane segmentation probabilities, cell
segmentation masks, and boundary masks, and outputs a probability score. As we
must process large data, this classifier only operates on cell boundaries, which
reduces computation over methods that analyze every pixel. For merge errors, we
invert and reuse the split classification network, instead asking it to rate a
set of generated candidate boundaries that hypothesize a split. %We compute
%corrections for both types of errors.

We also propose a greedy algorithm for guided proofreading. Possible erroneous
regions are sorted by their score, and a candidate correction is generated for each
region. Then, a user works through this list of regions and corrections. In a
forced choice setting, the user either selects a correction or skips it to
advance to the next region. In an automatic setting, errors with a high
probability are automatically corrected first, given an appropriate
probability threshold, after which the user would take over. Finally, to test
the limits of performance, we create an oracle which only accepts corrections
that improve the segmentation, based on knowledge of the ground truth. This is
guided proofreading with a perfect user.

@@

This paper makes the following contributions.
%
First, we present a CNN-based boundary classifier for split errors, plus a merge
error classifier that inverts the split error classifier. This is used to
propose merge error corrections, removing the need to manually draw the missing
edge. These classifiers perform well without much training data, which is
expensive to collect for connectomics data.
%
Second, we developed a guided proofreading approach to correcting segmentation
volumes, and an assessment scenario comparing forced-choice interaction with
automatic and oracle proofreading.
%
Third, we present the results of a quantitative user study assessing
guided proofreading. Our method is able to reduce segmentation
error faster than state-of-the-art semi-automatic tools for both novice and
expert users.

Guided proofreading is applicable to all existing automatic segmentation methods that
produce a label map. As such, we believe that our approach is a promising
direction to proofread segmentations more efficiently and better tackle large
volumes of connectomics imagery.

### 2016-11-15 paper/related_work.tex
Review changes; minor issues.

It is also possible to learn segmentation classification features directly from images with CNNs. Ronneberger \etal~\cite{RonnebergerFB15} use a contracting/expanding CNN path architecture to enable precise boundary localization with small amounts of training data. Lee \etal~\cite{lee2015recursive} recursively train very deep networks with 2D and 3D filters to detect boundaries.
%
All these approaches make good progress; however, in general, proofreading is still required to correct errors.
\\~\\
\textbf{Interactive Proofreading.} While proofreading is very time consuming, it is fairly easy for humans to perform corrections through splitting and merging segments. One expert tool is Raveler, introduced by Chklovskii~\etal~\cite{chklovskii2010, raveler}. Raveler is used today by professional proofreaders, and it offers many parameters for tweaking the process. Similar systems exist as products or plugins to visualization systems,~\eg V3D~\cite{proofreading_bottleneck} or AVIZO~\cite{markus_proofreading}.

@@

Between expert systems and online games sit Mojo and Dojo, by Haehn
\etal~\cite{haehn_dojo_2014,Neuroblocks}, which use simple scribble interfaces
for error correction. Dojo extends this to distributed proofreading via a
minimalistic web-based user interface. The authors define requirements for
general proofreading tools, and then evaluate the accuracy and speed of Raveler,
Mojo, and Dojo through a quantitative user study (Sec. 3 and
4)~\cite{haehn_dojo_2014}. Dojo had the highest performance. In this paper, we
use Dojo as a baseline for interactive proofreading.

All interactive proofreading solutions require the user to find potential errors manually, which takes the majority of time~\cite{proofreading_bottleneck,haehn_dojo_2014}. Recent papers propose computer-aided proofreading systems which help reduce the time spent in this visual search task.
\\~\\
\textbf{Computer-aided Proofreading.} Uzunbas \etal~\cite{uzunbas} showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method. The authors track uncertainty throughout the automatic labeling by training a conditional random field. This segmentation technique produces uncertainty estimates, which inform potential regions for proofreading to the user. While this applies to isotropic volumes, more work is needed to apply it to anisotropic volumes that exist for most connectomics datasets.

@@

Karimov \etal~\cite{karimov_guided_volume_editing} propose guided volume editing, which measures the difference in histogram distributions in image data to find potential split and merge errors in the corresponding segmentation. This lets expert users correct labeled computer-tomography datasets, using several interactions per correction. To correct merge errors, the authors create a large number of superpixels within a single segment and then successively group them based on dissimilarities. We were inspired by this approach but generate single watershed boundaries to handle the intracellular variance in high-resolution EM images (Sec.~\ref{sec:methods}).

Most closely related to our approach is the work of
Plaza~\cite{focused_proofreading}, who proposed \textit{focused proofreading}.
This method generates affinity scores by analyzing a region adjacency graph
across slices, then finds the largest affinities based on a defined impact
score. This yields edges of potential split errors which can be presented to the
proofreader. Plaza reports that additional manual work is required to find and
correct merge errors. Focused proofreading builds upon
NeuroProof~\cite{neuroproof2013} as its agglomerator, and is open source with
integration into Raveler. As the closest related work, we wish to use this
method as a baseline to evaluate our approach (Sec.~\ref{sec:evaluation}).
However, we separate the backend affinity score calculation from the
expert-level front end, and present our own user-friendly interface
(Sec.~\ref{sec:evaluation}).

>>>>

It is also possible to learn segmentation classification features directly from images with CNNs. Ronneberger \etal~\cite{RonnebergerFB15} use a contracting/expanding CNN path architecture to enable precise boundary localization with small amounts of training data. Lee \etal~\cite{lee2015recursive} recursively train very deep networks with 2D and 3D filters to detect boundaries.
%
All these approaches make good progress; however, in general, proofreading is still required to correct errors.
\\~\\
\textbf{Interactive Proofreading.} While proofreading is very time consuming, it is fairly easy for humans to perform corrections through splitting and merging segments. One expert tool is Raveler, introduced by Chklovskii~\etal~\cite{chklovskii2010, raveler}. Raveler is used today by professional proofreaders, and it offers many parameters for tweaking the process. Similar systems exist as products or plugins to visualization systems,~\eg, V3D~\cite{proofreading_bottleneck} and AVIZO~\cite{markus_proofreading}.

@@

Between expert systems and online games sit Mojo and Dojo, by Haehn
\etal~\cite{haehn_dojo_2014,Neuroblocks}, which use simple scribble interfaces
for error correction. Dojo extends this to distributed proofreading via a
minimalistic web-based user interface. The authors define requirements for
general proofreading tools, and then evaluate the accuracy and speed of Raveler,
Mojo, and Dojo through a quantitative user study (Sec.~3 and
4, ~\cite{haehn_dojo_2014}). Dojo had the highest performance. In this paper, we
use Dojo as a baseline for interactive proofreading.

All interactive proofreading solutions require the user to find potential errors manually, which takes the majority of the time~\cite{proofreading_bottleneck,haehn_dojo_2014}. Recent papers propose computer-aided proofreading systems to reduce the time spent in this visual search task.
\\~\\
\textbf{Computer-aided Proofreading.} Uzunbas \etal~\cite{uzunbas} showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method. The authors track uncertainty throughout the automatic labeling by training a conditional random field. This segmentation technique produces uncertainty estimates, which inform potential regions for proofreading to the user. While this applies to isotropic volumes, more work is needed to apply it to the typically anisotropic connectromics dataset volumes.

@@

Karimov \etal~\cite{karimov_guided_volume_editing} propose guided volume editing, which measures the difference in histogram distributions in image data to find potential split and merge errors in the corresponding segmentation. This lets expert users correct labeled computer-tomography datasets, using several interactions per correction. To correct merge errors, the authors create a large number of superpixels within a single segment and then successively group them based on dissimilarities. We were inspired by this approach, but instead we generate single watershed boundaries to handle the intracellular variance in high-resolution EM images (Sec.~\ref{sec:methods}).

Most closely related to our approach is the work of
Plaza~\cite{focused_proofreading}, who proposed \textit{focused proofreading}.
This method generates affinity scores by analyzing a region adjacency graph
across slices, then finds the largest affinities based on a defined impact
score. This yields edges of potential split errors which can be presented to the
proofreader. Plaza reports that additional manual work is required to find and
correct merge errors. Focused proofreading builds upon
NeuroProof~\cite{neuroproof2013} as its agglomerator, and is open source with
integration into Raveler. As the closest related work, we wish to use this
method as a baseline to evaluate our approach (Sec.~\ref{sec:evaluation}).
However, we separate the backend affinity score calculation from the Raveler
expert-level front end, and present our own novice-friendly interface
(Sec.~\ref{sec:evaluation}).
